\thetitle

### 2021-03-02 writing/landscape.tex
landscape, why-rational: fix mistakes in my previous changes

As a result, the call to \texttt{typed-pack} does {\em not\/} signal an error
because it takes place in the untyped {\tt client} module, which is compiled in
the usual manner. Later, when {\tt pack} is called in the {\tt crypto-pack-lib}
module, Transient's inlined checks make sure that the imported
\texttt{pack} is a function and that its result is a list. This
last check fails in \texttt{client}'s call to {\tt crypto-pack}.

@@

The following table summarizes the illustration:
%% -----------------------------------------------------------------------------
\begin{center}
\begin{tabular}{l|ll}
                        &        \multicolumn{2}{|c}{the evaluation of} \\
\relax                  & {\tt public-data}               & {\tt secret-data} in {\tt client}, \\
{under the $\cdot$ semantics yields} & & \\ \hline
%% ----------------------------------------------------------------------------------------
\qquad {\it Natural\/}   & error, blaming {\tt pack-lib}  & error, blaming {\tt pack-lib} \\
     		   	 &                                & \\
\qquad {\it Transient\/} & no error   		          & error, blaming the boundary \\
      		  	 &    			          & \quad {\tt pack-lib}/{\tt crypto-pack-lib} \\
\qquad {\it Erasure\/}   & no error 		          & no error \\
\end{tabular}
\end{center}
%% -----------------------------------------------------------------------------

>>>>

As a result, the call to \texttt{typed-pack} does {\em not\/} signal an error
because it takes place in the untyped {\tt client} module, which is compiled in
the usual manner. Because {\tt pack} is called in the {\tt crypto-pack-lib}
module, Transient's inlined checks make sure that the imported
\texttt{pack} is a function and that its result is a list. This
last check fails in \texttt{client}'s call to {\tt crypto-pack}.

@@

The following table summarizes the illustration:
%% -----------------------------------------------------------------------------
\begin{center}
\begin{tabular}{l|ll}
                        &        \multicolumn{2}{|c}{the evaluation of} \\
\relax                  & {\tt public-data}               & {\tt secret-data} in {\tt client}, \\
{under the $\cdot$ semantics yields} & & \\ \hline
%% ----------------------------------------------------------------------------------------
\qquad {\it Natural\/}   & error, blaming {\tt pack-lib}  & error, blaming {\tt pack-lib} \\
     		   	 &                                & \\
\qquad {\it Transient\/} & no error   		          & error, blaming the boundary \\
      		  	 &    			          & \quad {\tt pack-lib}/{\tt crypto-pack-lib} \\
\qquad {\it Erasure\/}   & no error 		          & no error \\
       	    		 &   \multicolumn{2}{|c}{but {\em Erasure} does signal an error on list access}
\end{tabular}
\end{center}
%% -----------------------------------------------------------------------------
